---
title: "Interaction View"
lib-dir: site_libs
params:
  AMGABID: "default"
format:
  html:
    include-in-header: header.html
    grid:
      sidebar-width: 50px
      body-width: 1700px
      margin-width: 50px
---

```{r,echo=FALSE}
source("helpers.R")

dat <- read.csv("data/Interactions.csv")

quarto::write_yaml_metadata_block(
  title = params[["AMGABID"]]
)

part_dat <- dat[dat[["AMGABID"]] == params[["AMGABID"]], ]
```

## Amyloid

Amyloid AmyloGraph ID (AGAMYID): `r markdown_link(part_dat[["AGAMYID"]], "../amyloids/", ".html")`.

Amyloid UniProt ID: `r markdown_uniprot(part_dat[["Amyloid.UniProt.ID"]])`.

## Antibody 

Antibody AmyloGraph ID (ABID): `r markdown_link(part_dat[["ABID"]], "../antibodies/", ".html")`.

Antibody names (as used in the reporting publication): `r np(part_dat[["Antibody.Name..if.not.INN."]])`.

## Interaction

Experimental model: `r np(part_dat[["Experimental.Model"]])`.

Experimental method: `r np(part_dat[["Experimental.method"]])`.

Amyloid epitope: `r np(part_dat[["Amy.epitope"]])`.

Amyloid.species.identified: `r np(part_dat[["Amyloid.species.identified"]])`.

Paratope/CDR/Negative.control: `r np(part_dat[["Ab.Paratope.CDR...Negative.control"]])`.

### Impact of the antibody on amyloid formation

In the case of more than one impact, they result from all the experiments present in a study.

```{r,echo=FALSE, results='asis'}
cat(paste0("  - ", unlist(strsplit(part_dat[["Impact.of.the.antibody.on.amyloid.formation"]], ", "))), sep = "\n\n")
```

## Source

DOI: `r markdown_doi(part_dat[["DOI"]])`.

PMID: `r markdown_pmid(part_dat[["PMID"]])`.
